Massively Parallel Monte Carlo Methods for Discrete Linear and Nonlinear Systems

### 2012-11-05 doc/prelim/presentation/prelim_presentation.tex
updating krylov slide
fixed typo
cleaning up krylov slides

  \medskip \medskip
  \begin{beamerboxesrounded}[upper=boxheadcolor,lower=boxbodycolor,shadow=true]
    {Search Subspace $\mathcal{K}$} Extract the solution from the
    search subspace:
    \[
    \tilde{\ve{x}} = \ve{x}_0 +
    \boldsymbol{\delta},\ \boldsymbol{\delta} \in \mathcal{K}
    \]
  \end{beamerboxesrounded}

  \medskip \medskip
  \begin{beamerboxesrounded}[upper=boxheadcolor,lower=boxbodycolor,shadow=true]
    {Constraint Subspace $\mathcal{L}$} Constrain the extraction with
    the constraint subspace by asserting orthogonality with the
    residual:
    \[
    \langle \tilde{\ve{r}},\ve{w} \rangle = 0,\ \forall \ve{w} \in
    \mathcal{L}
    \]  
  \end{beamerboxesrounded}

@@

  \medskip \medskip \medskip
  \small{
  \begin{itemize}
  \item Yields the normal system $\ve{A}^T\ve{A}\ve{x} =
    \ve{A}^T\ve{b}$
    \medskip
  \item Require only the action of the operator
    \medskip
  \item Must generate an orthonormal basis for
    $\mathcal{K}_m(\ve{A},\ve{r}_0)$
    \medskip
  \item Typically choose a Gram-Schmidt-like procedure such as Arnoldi
    or Lanzcos
    \medskip
  \item Short and long recurrence relations available for
    orthogonalization
  \end{itemize}
  }

@@

  \begin{itemize}
  \item Widely used in practice
    \medskip
  \item Krylov methods require only the action of the operator
    \medskip
  \item Parallelism achieved through a handful of operations
    \medskip
  \item Global reduction operations observed not to impede scalability
    (Gropp,2001)
    \begin{itemize}
    \item Dot product
    \item Vector norms
    \end{itemize}
    \medskip
  \item Nearest neighbor computations have poor algorithmic strong
    scaling
    \begin{itemize}
    \item Matrix-vector multiply
    \item Weak scaling is better
    \end{itemize}
    \medskip
  \item Short and long recurrence relations available for
    orthogonalization
  \end{itemize}

@@

%%---------------------------------------------------------------------------%%
\begin{frame}{Acknowledgements}

>>>>

  \medskip \medskip
  \begin{beamerboxesrounded}[upper=boxheadcolor,lower=boxbodycolor,shadow=true]
    {Search Subspace $\mathcal{K}$} Extract the solution to
    $\ve{A}\ve{x}=\ve{b}$ from the search subspace:
    \[
    \tilde{\ve{x}} = \ve{x}_0 +
    \boldsymbol{\delta},\ \boldsymbol{\delta} \in \mathcal{K}
    \]
  \end{beamerboxesrounded}

  \medskip \medskip
  \begin{beamerboxesrounded}[upper=boxheadcolor,lower=boxbodycolor,shadow=true]
    {Constraint Subspace $\mathcal{L}$} Constrain the extraction with
    the constraint subspace by asserting orthogonality with the
    residual ($\ve{r} = \ve{b}-\ve{A}\ve{x}$):
    \[
    \langle \tilde{\ve{r}},\ve{w} \rangle = 0,\ \forall \ve{w} \in
    \mathcal{L}
    \]  
  \end{beamerboxesrounded}

@@

  \medskip \medskip \medskip
  \small{
  \begin{itemize}
  \item Yields the normal system $\ve{A}^T\ve{A}\ve{x} =
    \ve{A}^T\ve{b}$
    \medskip
  \item Require only the action of the operator
    \medskip
  \item Must generate an orthonormal basis for
    $\mathcal{K}_m(\ve{A},\ve{r}_0)$
    \begin{itemize}
    \item Typically choose a Gram-Schmidt-like procedure such as Arnoldi
      or Lanzcos
    \item Short and long recurrence relations available for
      orthogonalization
    \end{itemize}
  \end{itemize}
  }

@@

  \begin{itemize}
  \item Global reduction operations observed not to impede scalability
    (Gropp,2001)
    \begin{itemize}
    \item Dot product
    \item Vector norms
    \end{itemize}
    \medskip
  \item Nearest neighbor computations have poor algorithmic strong
    scaling
    \begin{itemize}
    \item Matrix-vector multiply
    \item Weak scaling is better
    \end{itemize}
    \medskip
  \item Widely used in practice
    \medskip
  \item Krylov methods require only the action of the operator
    \medskip
  \item Parallelism achieved through a handful of operations
    \medskip
  \item Short and long recurrence relations available for
    orthogonalization
  \end{itemize}

@@

%%---------------------------------------------------------------------------%%
\begin{frame}{Acknowledgments}
